Three Algorithms for Merging Hierarchical Navigable Small World Graphs

### 2025-05-04 paper/main.tex
add to conclusion fact that merge can be used of fast graph construction

% TODO И тут надо сказать, что нас удивило, что ITGM показал лучшую производительность, чем CTGM. Поскольку мы ожидали, что CTGM будет производительно из того, что он имеет возможность выбирать следущую "опорную" вершину среди обеих графов и имеет меньше шансов застрять, и следовательно сделать меньше дорогостоящих операций полного поиска. По всей видимости выбор "главной" вершины в CGTM слишком дорогая операцией. И эти затраты не окупаются, сокращением числа полных поисков при "застревании".

@@

Finally, the researchers can focus on the idea that the neighborhood construction can be done for the set of vertex close to each other instead of forming neighborhood for one vertex per iteration. This can be more suitable for GPU or NPU settings.

@@

>>>>

@@

Also, the researchers can focus on the idea that the neighborhood construction can be done for the set of vertex close to each other instead of forming neighborhood for one vertex per iteration. This can be more suitable for GPU or NPU settings.

@@

Finally, future work can be applied to develop a fast graph construction procedure using one of the merge algorithms. It seems very naturally to start from the set of small graphs and merge them in a recursive manner.
